Assessing the Accessibility of Protein Tunnels using Motion Planning

### 2017-09-10 paper.tex
rrt description back in RW

Rapidly Exploring Random Tree (RRT)~\cite{lavalleRRT} is a single-query sampling-based motion planning method that 
incrementally builds a configuration tree rooted at the initial configuration.
%In each iteration of RRT, a random configuration $\qrand \in \C$ is generated and its nearest node $\qnear \in \T$ in the tree is found.
%A new configuration $\qnew$ is constructed on the line connecting $\qnear$ and $\qrand$ in the distance $\varepsilon$ from $\qnear$.
%If $\qnew$ is collision-free, it is added to the tree.
%The algorithm terminates if the tree approaches the goal configuration close enough.

>>>>

Rapidly Exploring Random Tree (RRT)~\cite{lavalleRRT} is a single-query sampling-based motion planning method that 
incrementally builds a configuration tree rooted at the initial configuration.
In each iteration of RRT, a random configuration $\qrand \in \C$ is generated and its nearest node $\qnear \in \T$ in the tree is found.
A new configuration $\qnew$ is constructed on the line connecting $\qnear$ and $\qrand$ in the distance $\varepsilon$ from $\qnear$.
If $\qnew$ is collision-free, it is added to the tree.
The algorithm terminates if the tree approaches the goal configuration close enough.

%In each iteration of RRT, a random configuration $\qrand \in \C$ is generated and its nearest node $\qnear \in \T$ in the tree is found.
%A new configuration $\qnew$ is constructed on the line connecting $\qnear$ and $\qrand$ in the distance $\varepsilon$ from $\qnear$.
%If $\qnew$ is collision-free, it is added to the tree.
%The algorithm terminates if the tree approaches the goal configuration close enough.
